```{r}
require(jpeg)
require(png)
require(COMP121)
puppy <- readPNG(getURLContent("http://dtkaplan.github.io/ScientificComputing/Resources/Images/mindo.png"))
canvas(x = c(1, 220), y = c(1, 220), asp = 1)
rasterImage( puppy, 1, 1, 216, 198)
#Cropping Tasks
canvas(x = c(1, 220), y = c(1, 220), asp = 1)
rasterImage( puppy[20:100,100:180,], 1, 1, 216, 198)
canvas(x = c(1, 220), y = c(1, 220), asp = 1)
rasterImage( puppy[140:198,1:40,], 1, 1, 216, 198)
canvas(x = c(1, 220), y = c(1, 220), asp = 1)
rasterImage( puppy[115:140,100:120,], 1, 1, 216, 198)
canvas(x=c(1,1000),y=c(1,1000))

new<-readJPEG(getURLContent("http://wholles.com/wp-content/uploads/2013/08/Cool-Wallpaper-HD.jpg"))
dim(new)
rasterImage(new,1,1,1000,1000)
canvas(x=c(1,1200),y=c(1,1200),asp=1)
new2<-new[,,1]
new3<-cbind(new2[,1:100],new2,new2[,900:1000])
rasterImage(new3,1,1,1200,1200)

framer<-function(picture,width){
  picture2<-picture[,,1]
  r<-dim(picture2)[1]
  col<-dim(picture2)[2]
  canvas(x=c(1,col+width),y=c(1,r+width),asp=1)
  picture3<-cbind(picture2[,rev(1:width)],picture2,picture2[,rev((col-width):col)])
  picture4<-rbind(picture3[rev(1:width),],picture3,picture3[rev((r-width):r),])
  rasterImage(picture4,1,1,r,col)
}

framer(new,100)


framer2<-function(picture,width){
  red<-picture[,,1]
  green<-picture[,,2]
  blue<-picture[,,3]
  r<-dim(picture)[1]
  col<-dim(picture)[2]
  canvas(x=c(1,col+width),y=c(1,r+width),asp=1)
  picture3<-cbind(red[,rev(1:width)],red,red[,rev((col-width):col)])
  picture4<-rbind(picture3[rev(1:width),],picture3,picture3[rev((r-width):r),])
  picture5<-cbind(green[,rev(1:width)],green,green[,rev((col-width):col)])
  picture6<-rbind(picture5[rev(1:width),],picture5,picture5[rev((r-width):r),])
  picture7<-cbind(blue[,rev(1:width)],blue,blue[,rev((col-width):col)])
  picture8<-rbind(picture7[rev(1:width),],picture7,picture7[rev((r-width):r),])
  bannanas<-array(c(picture6,picture8,picture4),dim=c(dim(picture6),3))

  rasterImage(bannanas,1,1,r,col)
}


framer2(new,0)
framer2(new,100)

```

```{r}
 framer3<-function(picture,width,negative=FALSE){
  red<-picture[,,1]
  green<-picture[,,2]
  blue<-picture[,,3]
  r<-dim(picture)[1]
  col<-dim(picture)[2]
  # take the negative image when appropriate
  f <- function(x) {
    if(negative) (1-x)
    else return(x)
  }
  canvas(x=c(1,col+width),y=c(1,r+width),asp=1)
  picture3<-cbind(
    f(red[,rev(1:width)]),
    red,f(red[,rev((col-width):col)]))
  picture4<-rbind(
    f(picture3[rev(1:width),])
    ,picture3,f(picture3[rev((r-width):r),]))
  picture5<-cbind(green[,rev(1:width)],green,green[,rev((col-width):col)])
  picture6<-rbind(picture5[rev(1:width),],picture5,picture5[rev((r-width):r),])
  picture7<-cbind(blue[,rev(1:width)],blue,blue[,rev((col-width):col)])
  picture8<-rbind(picture7[rev(1:width),],picture7,picture7[rev((r-width):r),])
  bannanas<-array(c(picture6,picture8,picture4),dim=c(dim(picture6),3))

  rasterImage(bannanas,1,1,r,col)
}
framer3(new,100,negative=TRUE)
```

framerC<-function(picture,width,Green=TRUE,Blue=TRUE,Red=TRUE){
  red<-picture[,,1]
  green<-picture[,,2]
  blue<-picture[,,3]
  r<-dim(picture)[1]
  col<-dim(picture)[2]
  canvas(x=c(1,col+width),y=c(1,r+width),asp=1)
  ifelse(Red==TRUE,picture3<-cbind(red[,rev(1:width)],red,red[,rev((col-width):col)])
  picture4<-rbind(picture3[rev(1:width),],picture3,picture3[rev((r-width):r),]),NA)
  ifelse(Green==TRUE,picture5<-cbind(green[,rev(1:width)],green,green[,rev((col-width):col)])
  picture6<-rbind(picture5[rev(1:width),],picture5,picture5[rev((r-width):r),]),NA)
  ifelse(Blue==TRUE,picture7<-cbind(blue[,rev(1:width)],blue,blue[,rev((col-width):col)])
  picture8<-rbind(picture7[rev(1:width),],picture7,picture7[rev((r-width):r),]),NA)
  bannanas<-array(c(picture6,picture8,picture4),dim=c(dim(picture6),3))

  rasterImage(bannanas,1,1,r,col)
}

framerC(new,100,Green=FALSE,Blue=TRUE,Red=TRUE)





```